Optimal (Multiway) Spatial Joins

### 2024-05-25 msj.tex
yufei

We will utilize the sets $\contained_{R_{k-2}}(h^*)$ of the segments $h^*$ in $H^*$, where $\contained_{R_{k-2}}(h^*)$ --- defined in \eqref{eqn:contained} --- is the set of rectangles in $R_{k-2}$ containing $h^*$. The next lemma is proven in Appendix~\ref{app:hv}.

@@

@@

\extraspacing {\bf Computing the ``$\bm{\contained_{R_{k-2}}(t)}$'' Sets.} We are ready to produce $\contained_{R_{k-2}}(h^*)$, defined in \eqref{eqn:type2:contained-t}, for any $\bm{t} \in \J(R_1, ..., R_{k-3}, H', V)$, based on Statement (2) of Lemma~\ref{lmm:hv:type2:contained-h*}. First, fetch the (already computed) minimal segment $h^*$ of $h'$ in $O(1)$ time. Then, scan the rectangles $r$ in $\contained_{R_{k-2}}(h^*)$ in descending order of $\xright(r)$. For each $r$ scanned, check whether $r \in 
\contained_{R_{k-2}}(\bm{t})$, or equivalently, whether $r$ covers the intersection point between $h$ and $v$; this takes $O(1)$ time. Abort the scan as soon as $r \notin 
\contained_{R_{k-2}}(\bm{t})$. This way, we compute $\contained_{R_{k-2}}(t)$ in $O(k + |\contained_{R_{k-2}}(t)|)$ time. Doing so for all $\bm{t} \in \J(R_1, ..., R_{k-3}, H', V)$ takes $O(k \cdot |\J| + \sum_\bm{t} |\contained_{R_{k-2}}(t)|) = O(k \cdot \out)$ time, where the derivation used Lemma~\ref{lmm:hv:type2:recur-output} and statement (3) of Lemma~\ref{lmm:hv:type2:properties}.

>>>>

We will utilize the sets $\contained_{R_{k-2}}(h^*)$ of the segments $h^*$ in $H^*$, where $\contained_{R_{k-2}}(h^*)$ --- defined in \eqref{eqn:contained} --- is the set of rectangles in $R_{k-2}$ containing $h^*$. These sets have some useful properties:

@@

The proof can be found in Appendix~\ref{app:hv}.

@@

\extraspacing {\bf Computing the ``$\bm{\contained_{R_{k-2}}(t)}$'' Sets.} We are ready to produce $\contained_{R_{k-2}}(h^*)$, defined in \eqref{eqn:type2:contained-t}, for any $\bm{t} \in \J(R_1, ..., R_{k-3}, H', V)$, based on Statement (2) of Lemma~\ref{lmm:hv:type2:contained-h*}. First, fetch the (already computed) minimal segment $h^*$ of $\bm{t}[k-2]$ in $O(1)$ time. Then, scan the rectangles $r$ in $\contained_{R_{k-2}}(h^*)$ in descending order of $\xright(r)$. For each $r$ scanned, check whether $r \in 
\contained_{R_{k-2}}(\bm{t})$, or equivalently, whether $r$ covers the intersection point between $h$ and $v$; this takes $O(1)$ time. Abort the scan as soon as $r \notin 
\contained_{R_{k-2}}(\bm{t})$. This way, we compute $\contained_{R_{k-2}}(t)$ in $O(k + |\contained_{R_{k-2}}(t)|)$ time. Doing so for all $\bm{t} \in \J(R_1, ..., R_{k-3}, H', V)$ takes $O(k \cdot |\J| + \sum_\bm{t} |\contained_{R_{k-2}}(t)|) = O(k \cdot \out)$ time, where the derivation used Lemma~\ref{lmm:hv:type2:recur-output} and statement (3) of Lemma~\ref{lmm:hv:type2:properties}.
